\textit{Red Oak}\\ Proactive Controller Generation for Algorithmic Policy

### 2015-05-11 draft.tex
final edits

\subsection*{A.P.I.}
In our programming model, algorithmic policies interact with packets through API function calls before returning a forwarding decision. We include in Figure~\ref{fig:range_api} the core of our \lstinline|API.|.

@@

\section*{Related Work}
% deeper comparison with Maple

%???

\section*{Future Work and Conclusion}
In this paper, we have introduced Oak, a SDN library for proactively switch forwarding rules
from an arbitrary programmer-defined policy in a general purpose programming language.
Oak provides programmers the abstraction that their centralized policy will run on each 
new packet entering the network, while alleviating for the programmer need to consider
how to split the decision logic between to switches and the controller.

>>>>

\subsection*{A.P.I.}
In our programming model, algorithmic policies interact with packets through API function calls before returning a forwarding decision. We include in Figure~\ref{fig:range_api} the core of our \lstinline|API|.

@@

\section*{Related Work}
There are a number of existing programming abstractions for SDN. The Frenetic~\citep{Frenetic} family of languages provide domain-specific operators for composing packet processing functions together and compiling them to switches. Here we focus on compiling arbitrary programmer functions in a general-purpose language. Merlin~\cite{Merlin} is a language for configuring networks based on path and quality of service constraints. However, Merlin focuses mainly on stateless, static network configurations, whereas we focus on stateful, dynamic applications. Our work is most closely related to Maple~\citep{Maple}. Like Maple, we implement policies in a general purpose language, but rather than reactively memoizing decisions, we generate forwarding decision proactively through symbolic analysis.

\section*{Conclusion}
In this paper, we have introduced Oak, a SDN library for proactively switch forwarding rules
from an arbitrary programmer-defined policy in a general purpose programming language.
Oak provides programmers the abstraction that their centralized policy will run on each 
new packet entering the network, while alleviating for the programmer need to consider
how to split the decision logic between to switches and the controller.
